---
title: "Stats140SL Data Cleaning"
author: "Josh Kong"
date: "12/6/2020"
output: pdf_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Loading file and libraries
```{r}
library(tidyverse)
library(tidytext)
library(cluster)
listing <- read_csv("listings.csv")
```


## Data Cleaning

Just doing some really quick data cleaning
```{r}
#Getting the columns that we want
listings_df <- listing %>% 
  select(id, name, description, neighborhood_overview, host_id, price)

#taking a quick look at the dataset
head(listings_df)
skimr::skim(listings_df)

#parsing price column
listings_df$price <- parse_number(listings_df$price)
```

* Things to note: Description has 1007 NA values, and neighborhood_overview has 10572 NA values.


Maybe we can make this into a classfication problem? 

Use k means to create 3 clusters, low price, mid price, and high price. 

```{r}
listings_df %>% 
  filter(price < 500) %>% 
  ggplot(aes(price)) + 
  geom_histogram()

#make any pricing over $500 automatically high priced. Will do k means on listings less than $500 so that the data doesn't get skewed due to the outliers.
```

## K means clustering 3 clusters
```{r}
listings_cluster <- listings_df %>% 
  filter(price <= 500 ) #filtering out for pricings less than $500

set.seed(123)
pricing_cluster <- kmeans(listings_cluster$price, 3)
cluster_centers <- sort(pricing_cluster$centers)
pricing_cluster <- kmeans(listings_cluster$price, centers = cluster_centers)

#assigning the clusters
listings_cluster$value <- pricing_cluster$cluster

#joining all the data together
listings_c <- listings_cluster %>% 
  select(id, value)

listings <- listings_df %>% 
  left_join(listings_c, by = c("id"))

#filling in the values for pricings over $500
for(i in 1:nrow(listings)){
  if(is.na(listings$value[i]))
  {
    listings$value[i] <- 3
  }
}

#changing the label of the value from numbers to "high, medium, low"
for(i in 1:nrow(listings)){
  if(listings$value[i] == 1)
  {
    listings$value[i] <- "low"
  }
  else if(listings$value[i] == 2)
  {
    listings$value[i] <- "medium"
  }
  else{
    listings$value[i] <- "high"
  }
}

listings$value <- factor(listings$value)
```

Cleaning up the descriptions
```{r}
library(tidytext)
listings_cleaned <- listings %>% 
  mutate(description = str_remove_all(description, "\\<br \\/\\>"),
         description = str_remove_all(description, "\\<b\\>"),
         description = str_remove_all(description, "\\<\\/b\\>"),
         description = str_remove_all(description, "The space"),
         neighborhood_overview = str_remove_all(neighborhood_overview,"\\<br \\/\\>"),
         neighborhood_overview = str_remove_all(neighborhood_overview,"\\<b\\>"),
         neighborhood_overview = str_remove_all(neighborhood_overview,"\\<\\/b\\>"),
         neighborhood_overview = str_remove_all(neighborhood_overview,"The space"))


write.csv(listings_cleaned, "listings_cleaned_3clus.csv")
```

## K means clustering, 2 clusters

Re doing the clusters, but this time making it into only 2 clusters; high and low.

```{r}
listings_cluster2 <- listings_df %>% 
  filter(price <= 300 ) #filtering out for pricings less than $300

set.seed(123)
pricing_cluster2 <- kmeans(listings_cluster2$price, 2)
cluster_centers2 <- sort(pricing_cluster2$centers)
pricing_cluster2 <- kmeans(listings_cluster2$price, centers = cluster_centers2)

#assigning the clusters
listings_cluster2$value <- pricing_cluster2$cluster

#joining all the data together
listings_c2 <- listings_cluster2 %>% 
  select(id, value)

listings2 <- listings_df %>% 
  left_join(listings_c2, by = c("id"))

#filling in the values for pricings over $300
for(i in 1:nrow(listings2)){
  if(is.na(listings2$value[i]))
  {
    listings2$value[i] <- 2
  }
}

#changing the label of the value from numbers to "high, medium, low"
for(i in 1:nrow(listings2)){
  if(listings2$value[i] == 1)
  {
    listings2$value[i] <- "low"
  }
  else
  {
    listings2$value[i] <- "high"
  }
}

listings2$value <- factor(listings2$value)
```

Cleaning up descriptions

```{r}
listings_cleaned2 <- listings2 %>% 
  mutate(description = str_remove_all(description, "\\<br \\/\\>"),
         description = str_remove_all(description, "\\<b\\>"),
         description = str_remove_all(description, "\\<\\/b\\>"),
         description = str_remove_all(description, "The space"),
         neighborhood_overview = str_remove_all(neighborhood_overview,"\\<br \\/\\>"),
         neighborhood_overview = str_remove_all(neighborhood_overview,"\\<b\\>"),
         neighborhood_overview = str_remove_all(neighborhood_overview,"\\<\\/b\\>"),
         neighborhood_overview = str_remove_all(neighborhood_overview,"The space"))


write.csv(listings_cleaned2, "listings_cleaned_2clus.csv")
```









